\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-22 trunk/europa.tex
added resource envelopes figure.

\label{eu:model}
%\caption{Specifying a problem instance for the Shopping Agent in NDDL}
\end{verbatim}

@@

\comment{figure :provide snapshot of resource envelopes generated by europa}

@@

\item Open Condition: an open condition is an inactive token. Inactive
  tokens can be generated by explicitly posted goals, or when a token
  is activated, rules may fire that create inactive slave tokens
  \comment{reference: point to more detailed decription above in Rules
    Engine section}.  Open Conditions can be resolved in three ways:

@@

\begin{verbatim}
    public void solve(ConstraintEngine ce, int maxIter)
    {
    	curIter=0;

    	while ((ce.getViolations() > 0) && (curIter < maxIter)) {
	    Variable queenToMove = getQueenWithMaxViolation(ce);
    	     int curPos = queenToMove.getCurrentValue();

            SortedSet<int> moves = getMoves(ce,queenToMove,curPos);             
  	   boolean moved = false;
            for (int newPos : moves) {
            	moved = tryMove(queenToMove,curPos,newPos);
            	if (moved)
            	    break;
            }

            if (!moved) 
            	forceMove(queenToMove,curPos,moves.first());

            checkSolution(); // See if we have a new best solution            
            curIteration_++;
    	}
    }
\end{verbatim}

>>>>

\label{eu:model}
\end{verbatim}

@@

\begin{figure}
\centering
\includegraphics[scale=0.35]{figs/europa-resource-envelopes.png}
\caption{\small Resource Envelopes computed by  \eu}
\label{fig:resenvelopes}
\vskip+0.1cm
\end{figure}

@@

\item Open Condition: an open condition is an inactive token. Inactive
  tokens can be generated by explicitly posted goals, or when a token
  is activated, rules may fire that create inactive slave tokens as described in section
  \comment{point to EUROPA Plan Representation section}.  Open Conditions can be resolved in three ways:

@@

\begin{algorithm}[H]
  \KwIn{ConstraintEngine $ce$}
  \KwIn{int $maxIter$}
  \Begin{
    int $curIter \leftarrow 0$ \;
    \While{$\left( ce.getViolations() > 0 \right) ~ \& ~ \left( curIter <
        maxIter \right)$ }{
      Variable $queenToMove \leftarrow getQueenWithMaxViolation(ce)$
      \;
      SortedSet$<$int$> moves \leftarrow getMoves(ce, queenToMove,
      curPos)$ \;
      bool $moved \leftarrow $ \texttt{false} \;
      \ForEach{int $newPos$ of $moves$}{
        $moved \leftarrow tryMove(queenToMove, curPos, newPos)$\;
        \lIf{$moved$}{ \textbf{break} \; }
      }
      \lIf{$! moved$}{
        $forceMove(queenToMove, curPos, moves.first())$ \;
      }
      $checkSolution()$ \tcp*{See if we have a new best solution}
      $curIter$\texttt{++} \;
    }
  }
  \caption{$solveNQueens(ce, maxIter)$}
\end{algorithm}
